Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging

### 2023-01-06 script/manuscript_MEE.Rmd
possible mismatch with sequence classifications and sequence numbers

pmorph <- read.csv('../data/morpho_pollen.csv')
mertensia_samples <- pmorph %>% 
  group_by(sample.id) %>% 
  filter(morphotype == 'MERTENSIA') %>% 
  select(sample.id, sum)

@@

blst <- read.csv('../data/classified_blast.csv')

>>>>

pmorph <- read.csv('../data/morpho_pollen.csv')
mertensia_samples <- pmorph %>% 
  group_by(sample.id) %>% 
  mutate(Prop = sum/sum(sum)) %>% 
  filter(morphotype == 'MERTENSIA') %>% 
  select(sample.id, Prop, sum)

@@

blst <- read.csv('../data/classified_blast.csv') 
blst_seqs <- distinct(blst, sample.id) 
mertensia_samples <- filter(mertensia_samples, sample.id %in% blst_seqs$sample.id)

# # SOMETHING MUST BE VERY WRONG HERE, MISSED MERTENSIA IN NEARLY PURE SAMPLES. 
blst_mertensia <- blst %>% 
  filter(Genus == 'Mertensia') %>% 
  select(sample.id,  Prcnt_seqs) %>% 
  group_by(sample.id) %>% 
  mutate(Prcnt_seqs = sum(Prcnt_seqs)) %>% 
  distinct(sample.id, .keep_all = T)

mertensia_detected <- mertensia_samples %>% 
  mutate(DETECTED = if_else(sample.id %in% blst_mertensia$sample.id, 1, 0))

M1 <- glm(DETECTED ~ Prop, mertensia_detected, family = binomial)
M.df <- data.frame(Prop = seq(0, 100, 0.5))
M.df$DETECTED <- predict(M1, newdata=M.df, type="response")

ggplot(M.df, aes(x=Prop, y=DETECTED)) +
  stat_smooth(method="glm", se=T, fullrange=TRUE, 
              method.args = list(family=binomial))  +
  theme_bw()
